The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
rm potential

Animal social network analysis is a well-developed tool used to measure the
relationships of individuals and organization of social systems [@Krause_2009;
@Wey_2008; @Croft_2011]. Social network analysis provides insight into the
structure of social communities and social network properties, which can
influence population dynamics and evolutionary processes [@Pinter_Wollman_2013;
@Kurvers_2014]. Despite the widespread use and innovation of traditional social
network analysis [@Webber_2019], it typically considers a single scale of
sociality in a given network (monolayer), drastically simplifying the potential
complexity of animal social systems [@Finn_2019].

>>>>

Animal social network analysis is a well-developed tool used to measure the
relationships of individuals and organization of social systems [@Krause_2009;
@Wey_2008; @Croft_2011]. Social network analysis provides insight into the
structure of social communities and social network properties, which can
influence population dynamics and evolutionary processes [@Pinter_Wollman_2013;
@Kurvers_2014]. Despite the widespread use and innovation of traditional social
network analysis [@Webber_2019], it typically considers a single scale of
sociality in a given network (monolayer), drastically simplifying the
complexity of animal social systems [@Finn_2019].
